PBMC_Donor

### 2019-08-12 PBMC.Rmd
separated out pre and post og viabilities

grid.arrange(
    plot_pbmc(pbmc, "PreOG_Viability")+labs(y="Viability"),
    plot_pbmc(pbmc, "PreOG_Cells.Vial")+labs(y="Cells/Vial"),
    top=text_grob("Post OG Staining", size=20), ncol=2
)
```

>>>>

grid.arrange(
    plot_pbmc(pbmc, "PostOG_Viability")+labs(y="Viability"),
    plot_pbmc(pbmc, "PostOG_Cells.Vial")+labs(y="Cells/Vial"),
    top=text_grob("Post OG Staining", size=20), ncol=2
)
```
